### 2022-03-31 outputs/paper/paper.Rmd
clean data

---
title: "Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]"
subtitle: "Possible factors effecting 2016 election"
author: 
  - SangWoong Lee
  - Young Suk
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This paper has been examined possible variables that influenced U.S citizens' choice for the 2016 U.S presidential election. We have found that there exists significantly different opinions regarding gender, wealth, race and age. This is important in a sesne that it shows thought trends as well as crucial decision indicators for voting in U.S.,With further survey at the end of this paper, we are going to explore whether this is happening only in U.S or not."
output:
  bookdown::pdf_document2:
    fig_caption: yes
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(dplyr)
library(knitr)
```

# Introduction

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point).

# Data
```{r, include=FALSE, echo=FALSE}
# Read the extracted and cleaned data, data extraction done in 01-gather-data.R and modification done in 02-clean-and-prepare-data.R
data <- read_csv("outputs/data/cleaned_data.csv")
```

```{r}

```

Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

```{r}

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it.

# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional details

\newpage

# References

### 2022-03-31 scripts/01-gather_data.R

@@ -18,21 +18,6 @@ get_data <- function(text){
   immune_data <- immune_data[-c(19:20),]
   #immune_data <- extract(immune_data, raw_text, into=c('v1', 'v2'), '(\\d+)(\\D+)', convert=TRUE)
   
-  
-  # Grab the type of table
-  #gettype_of_table <- just_page_i[2] |> str_squish()
-  
-  # Get rid of the top matter
-  # Manually for now, but could create some rules if needed
-  # no_header <- text[7:length(text)]
-  
-  # Get rid of the bottom matter
-  # Manually for now, but could create some rules if needed
-  # table_header_no_footer <- no_header[1:25] 
-  
-  # Convert into a tibble
-  # demography_data <- tibble(all = table_header_no_footer)
-  
   # Split columns
   immune_data <-
     immune_data |>
@@ -42,6 +27,7 @@ get_data <- function(text){
     mutate(raw_text = str_replace(raw_text, "N Central", "Central")) |>
     mutate(raw_text = str_replace(raw_text, "No education", "NoEducation")) |>
     mutate(raw_text = str_replace(raw_text, "15-1", "15.1")) |>
+    mutate(raw_text = str_replace(raw_text, "Islan", "Islam")) |>
     separate(col = raw_text,
              into = c("Variable", "Health_Record", "Mothers_Report", "Received_Immunization", "Not_Received_Immunization", "Total_Percent", "Number_of_Children"),
              sep = " ", # Works fine because the tables are nicely laid out
@@ -55,34 +41,9 @@ get_data <- function(text){
     mutate_at(vars(Health_Record, Mothers_Report, Received_Immunization, Not_Received_Immunization, Total_Percent, Number_of_Children), ~str_remove_all(., ",")) |>
     #mutate_at(vars(Health_Record, Mothers_Report, Received_Immunization, Not_Received_Immunization, Total_Percent, Number_of_Children), ~str_replace(., "_", "0")) |>
     #mutate_at(vars(Health_Record, Mothers_Report, Received_Immunization, Not_Received_Immunization, Total_Percent, Number_of_Children), ~str_replace(., "-", "0")) |>
-    mutate_at(vars(Health_Record, Mothers_Report, Received_Immunization, Not_Received_Immunization, Total_Percent, Number_of_Children), ~as.double(.)) |>
-    column_to_rownames(var = "Variable")
[…]

### 2022-03-31 scripts/02-clean_and_prepare_data.R

@@ -14,8 +14,12 @@ extracted_data <- read_csv("inputs/data/extracted_data.csv")
 
 #### Data Cleaning ####
 
-# Only keep useful columns
-cleaned_data <- extracted_data %>%
-  select("Health_Record", "Mothers_Report", "Received_Immunization", "Not_Received_Immunization", "Number_of_Children")
+# Only keep useful columns by removing total percent column.
+cleaned_data <- extracted_data  |> select(-c(Total_Percent)) |>
+  column_to_rownames(var = "Variable")
+
+
+view(cleaned_data)
 
 #### Save ####
+write_csv(cleaned_data, "outputs/data/cleaned_data.csv")

### 2022-03-31 scripts/02-clean_and_prepare_data.R
data cleaning

@@ -15,8 +15,7 @@ extracted_data <- read_csv("inputs/data/extracted_data.csv")
 #### Data Cleaning ####
 
 # Only keep useful columns by removing total percent column.
-cleaned_data <- extracted_data  |> select(-c(Total_Percent)) |>
-  column_to_rownames(var = "Variable")
+cleaned_data <- extracted_data  |> select(-c(Total_Percent))
 
 
 view(cleaned_data)

### 2022-03-31 outputs/paper/paper.Rmd
data cleaning
ggplot

@@
 ```{r}
-
+data %>%
+  ggplot(aes(x = Variable, y = Health_Record)) +
+  geom_bar(stat='identity') +
+  coord_flip()
 ```
@@
 
-# This needs to be about the random data tha tI sasmpled?
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = FALSE) +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
 ```

### 2022-03-31 scripts/00-simulation.R
simulation

@@ -13,39 +13,102 @@ library(tidyverse)
 
 set.seed(777)
 sample_size <- 3000
-simulated_immunization_data <- 
+simulated_urban_rural <- 
   tibble(
     variables = 
       c(
         rep('Urban',1),
-        rep('Rural',1),
-        rep('North',1),
-        rep('Northeast',1),
-        rep('Central',1),
-        rep('South',1),
-        rep('Bangkok',1),
-        rep('No_education',1),
-        rep('Primary',1),
-        rep('Secondary',1),
-        rep('Higher',1),
-        rep('Buddhist',1),
-        rep('Islam',1)
+        rep('Rural',1)
       ),
     Health_record = 
-      runif(n=13,
+      runif(n=2,
             min = 0,
             max = 100),
     Mother_record = 
-      runif(n= 13,
+      runif(n= 2,
             min = 0,
             max = 100 -Health_record),
     immunization = Mother_record + Health_record,
     non_immunization = 100 - immunization,
     number_of_childeren = 
-      runif(n = 13,
+      runif(n = 2,
             min = 0,
             max = 3000) |> round()
   )
+simulated_region <- 
+  tibble(
+    variables = 
+      c(
+        rep('North',1),
+        rep('Northeast',1),
+        rep('Central',1),
+        rep('South',1),
+        rep('Bangkok',1)
+      ),
+    Health_record = 
+      runif(n=5,
+            min = 0,
+            max = 100),
+    Mother_record = 
+      runif(n= 5,
+            min = 0,
+            max = 100 -Health_record),
+    immunization = Mother_record + Health_record,
+    non_immunization = 100 - immunization,
+    number_of_childeren = 
+      runif(n = 5,
+            min = 0,
+            max = 3000) |> round()
+  )
+simulated_education <- 
+  tibble(
+    variables = 
+      c(
+        rep('No_education',1),
+        rep('Primary',1),
+        rep('Secondary',1),
+        rep('Higher',1)
+      ),
+    Health_record = 
+      runif(n=4,
+            min = 0,
+            max = 100),
+    Mother_record = 
+      runif(n= 4,
+            min = 0,
+            max = 100 -Health_record),
+    immunization = Mother_record + Health_record,
+    non_immunization = 100 - immunization,
+    number_of_childeren = 
+      runif(n = 4,
+            min = 0,
+            max = 3000) |> round()
+  )
+simulated_religion <- 
+  tibble(
+    variables = 
+      c(
[…]

### 2022-03-31 scripts/00-simulation.R
simulation

@@ -31,9 +31,7 @@ simulated_urban_rural <-
     immunization = Mother_record + Health_record,
     non_immunization = 100 - immunization,
     number_of_childeren = 
-      runif(n = 2,
-            min = 0,
-            max = 3000) |> round()
+      rmultinom(n = 1, size = 3000, prob = rep(1/2, 2))
   )
 simulated_region <- 
   tibble(
@@ -56,9 +54,7 @@ simulated_region <-
     immunization = Mother_record + Health_record,
     non_immunization = 100 - immunization,
     number_of_childeren = 
-      runif(n = 5,
-            min = 0,
-            max = 3000) |> round()
+      rmultinom(n = 1, size = 3000, prob = rep(1/5, 5))
   )
 simulated_education <- 
   tibble(
@@ -80,9 +76,7 @@ simulated_education <-
     immunization = Mother_record + Health_record,
     non_immunization = 100 - immunization,
     number_of_childeren = 
-      runif(n = 4,
-            min = 0,
-            max = 3000) |> round()
+      rmultinom(n = 1, size = 3000, prob = rep(1/4, 4))
   )
 simulated_religion <- 
   tibble(
@@ -102,9 +96,7 @@ simulated_religion <-
     immunization = Mother_record + Health_record,
     non_immunization = 100 - immunization,
     number_of_childeren = 
-      runif(n = 2,
-            min = 0,
-            max = 3000) |> round()
+      rmultinom(n = 1, size = 3000, prob = rep(1/2, 2))
   )
 
 simulated_immunization_data <- rbind(simulated_urban_rural, simulated_region, simulated_education, simulated_religion)

### 2022-03-31 scripts/00-simulation.R
Simulation and testing edit

@@ -98,8 +98,18 @@ simulated_religion <-
     number_of_childeren = 
       rmultinom(n = 1, size = 3000, prob = rep(1/2, 2))
   )
-
-simulated_immunization_data <- rbind(simulated_urban_rural, simulated_region, simulated_education, simulated_religion)
+simulated_total <- 
+  tibble(
+    variables = rep('total',1),
+    Health_record = (simulated_urban_rural$number_of_childeren[1] * (simulated_urban_rural$Health_record[1] *0.01)
+    + simulated_urban_rural$number_of_childeren[2] * (simulated_urban_rural$Health_record[2] *0.01)) / 3000 * 100,
+    Mother_record = (simulated_urban_rural$number_of_childeren[1] * (simulated_urban_rural$Mother_record[1] *0.01)
+                     + simulated_urban_rural$number_of_childeren[2] * (simulated_urban_rural$Mother_record[2] *0.01)) / 3000 * 100,
+    immunization = Mother_record + Health_record,
+    non_immunization = 100 - immunization,
+    number_of_childeren = 3000
+  )
+simulated_immunization_data <- rbind(simulated_urban_rural, simulated_region, simulated_education, simulated_religion,simulated_total)
   
 simulated_immunization_data$variables |>
   unique() == c('Urban',

### 2022-03-31 scripts/02-clean_and_prepare_data.R

@@ -17,7 +17,34 @@ extracted_data <- read_csv("inputs/data/extracted_data.csv")
 # Only keep useful columns by removing total percent column.
 cleaned_data <- extracted_data  |> select(-c(Total_Percent))
 
+### Test ###
+column_names_as_contracts <- 
+  cleaned_data |> 
+  rename(
+    "chr_variable" = "Variable",
+    "int_Health_Record" = "Health_Record",
+    "int_Mothers_Report" = "Mothers_Report",
+    "int_Received_Immunization" = "Received_Immunization",
+    "int_Not_Received_Immunization" = "Not_Received_Immunization",
+    "int_Childeren_Count" = "Number_of_Children",
+  )
+agent <-
+  create_agent(tbl = column_names_as_contracts) |>
+  col_is_character(columns = vars(chr_variable)) |>
+  col_is_numeric(columns = vars(int_Health_Record,int_Mothers_Report,int_Received_Immunization,
+                                int_Not_Received_Immunization,int_Childeren_Count)) |>
+  col_vals_between(vars(int_Health_Record),0,100) |>
+  col_vals_between(vars(int_Mothers_Report),0,100) |>
+  col_vals_between(vars(int_Received_Immunization),0,100) |>
+  col_vals_between(vars(int_Not_Received_Immunization),0,100) |>
+  col_vals_between(vars(int_Childeren_Count),0, 2872) |>
+  col_vals_in_set(columns = chr_variable,
+                  set = c("Urban", "Rural", "North","NorthEast","Central","South",
+                          "Bangkok","No Education","Primary","Secondary","Higher","Buddhist"
+                          ,"Islam","Total")) |>
+  interrogate()
 
+agent
 view(cleaned_data)
 
 #### Save ####

### 2022-03-31 scripts/02-clean_and_prepare_data.R
pointblank

@@ -9,6 +9,7 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(pointblank)
 # Read in the raw data. 
 extracted_data <- read_csv("inputs/data/extracted_data.csv")
 
@@ -27,7 +28,9 @@ column_names_as_contracts <-
     "int_Received_Immunization" = "Received_Immunization",
     "int_Not_Received_Immunization" = "Not_Received_Immunization",
     "int_Childeren_Count" = "Number_of_Children",
-  )
+  ) |>
+  mutate(total_calculated = int_Health_Record + int_Mothers_Report) |>
+  mutate(no_immune_calculated = 100 - int_Received_Immunization)
 agent <-
   create_agent(tbl = column_names_as_contracts) |>
   col_is_character(columns = vars(chr_variable)) |>
@@ -42,6 +45,8 @@ agent <-
                   set = c("Urban", "Rural", "North","NorthEast","Central","South",
                           "Bangkok","No Education","Primary","Secondary","Higher","Buddhist"
                           ,"Islam","Total")) |>
+  col_vals_equal(vars(total_calculated), vars(int_Received_Immunization))|>
+  col_vals_equal(vars(no_immune_calculated), vars(int_Not_Received_Immunization))|>
   interrogate()
 
 agent

### 2022-03-31 scripts/01-gather_data.R
data error correction

@@ -28,6 +28,7 @@ get_data <- function(text){
     mutate(raw_text = str_replace(raw_text, "No education", "NoEducation")) |>
     mutate(raw_text = str_replace(raw_text, "15-1", "15.1")) |>
     mutate(raw_text = str_replace(raw_text, "Islan", "Islam")) |>
+    mutate(raw_text = str_replace(raw_text, "10.6", "70.6")) |>
     separate(col = raw_text,
              into = c("Variable", "Health_Record", "Mothers_Report", "Received_Immunization", "Not_Received_Immunization", "Total_Percent", "Number_of_Children"),
              sep = " ", # Works fine because the tables are nicely laid out

### 2022-04-01 scripts/00-simulation.R
Simulation fixed (numeric error in children number)

@@ -31,7 +31,7 @@ simulated_urban_rural <-
     immunization = Mother_record + Health_record,
     non_immunization = 100 - immunization,
     number_of_childeren = 
-      rmultinom(n = 1, size = 3000, prob = rep(1/2, 2))
+      as.numeric(rmultinom(n = 1, size = 3000, prob = rep(1/2, 2)))
   )
 simulated_region <- 
   tibble(
@@ -54,7 +54,7 @@ simulated_region <-
     immunization = Mother_record + Health_record,
     non_immunization = 100 - immunization,
     number_of_childeren = 
-      rmultinom(n = 1, size = 3000, prob = rep(1/5, 5))
+      as.numeric(rmultinom(n = 1, size = 3000, prob = rep(1/5, 5)))
   )
 simulated_education <- 
   tibble(
@@ -76,7 +76,7 @@ simulated_education <-
     immunization = Mother_record + Health_record,
     non_immunization = 100 - immunization,
     number_of_childeren = 
-      rmultinom(n = 1, size = 3000, prob = rep(1/4, 4))
+      as.numeric(rmultinom(n = 1, size = 3000, prob = rep(1/4, 4)))
   )
 simulated_religion <- 
   tibble(
@@ -96,7 +96,7 @@ simulated_religion <-
     immunization = Mother_record + Health_record,
     non_immunization = 100 - immunization,
     number_of_childeren = 
-      rmultinom(n = 1, size = 3000, prob = rep(1/2, 2))
+      as.numeric(rmultinom(n = 1, size = 3000, prob = rep(1/2, 2)))
   )
 simulated_total <- 
   tibble(
@@ -125,7 +125,7 @@ simulated_immunization_data$variables |>
                 'Higher',
                 'Buddhist',
                 'Islam')
-simulated_immunization_data$variables |> unique() |> length() == 13
+simulated_immunization_data$variables |> unique() |> length() == 14
 simulated_immunization_data$Health_record |>  min() >= 0 
 simulated_immunization_data$Health_record |>  max() <= 100
 simulated_immunization_data$Mother_record |>  min() >= 0 

### 2022-04-01 outputs/paper/paper.Rmd
ggplot

@@
 ```{r}
-data %>%
-  ggplot(aes(x = Variable, y = Health_Record)) +
-  geom_bar(stat='identity') +
-  coord_flip()
+ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
 ```
-
+```{r}
+ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
+```
+```{r}
+ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
+```
+```{r}
+ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
+```
 Talk more about it.

### 2022-04-01 scripts/02-clean_and_prepare_data.R
pointblank

@@ -29,8 +29,9 @@ column_names_as_contracts <-
     "int_Not_Received_Immunization" = "Not_Received_Immunization",
     "int_Childeren_Count" = "Number_of_Children",
   ) |>
-  mutate(total_calculated = int_Health_Record + int_Mothers_Report) |>
-  mutate(no_immune_calculated = 100 - int_Received_Immunization)
+  mutate(total_calculated = round(int_Health_Record + int_Mothers_Report, 1)) |>
+  mutate(no_immune_calculated = round(100 - int_Received_Immunization, 1))
+
 agent <-
   create_agent(tbl = column_names_as_contracts) |>
   col_is_character(columns = vars(chr_variable)) |>

### 2022-04-02 outputs/paper/paper.Rmd
ggplot

--- 2022-03-31 outputs/paper/paper.Rmd
@@
 data <- read_csv("outputs/data/cleaned_data.csv")
+
+# create new dataset only for urban-rural data
+urban_rural <- data.frame(location = c(rep("urban", data[1,6]), rep("rural", data[2,6])),
+                immune_data =  c(rep("Health Report", round(data[1,2]*data[1,6]/100)), rep("Mothers Report", round(data[1,3]*data[1,6]/100)), rep("No immune", round(data[1,5]*data[1,6]/100)), 
+                                 rep("Health Report", round(data[2,2]*data[2,6]/100)), rep("Mothers Report", round(data[2,3]*data[2,6]/100)), rep("No immune", round(data[2,5]*data[2,6]/100)))
+
+                )
+
+# create new dataset only for for region
+region <- data.frame(region = c(rep("north", data[3,6]), rep("north_east", data[4,6]), rep("central", data[5,6]), rep("south", data[6,6]), rep("bangkok", data[7,6])),
+                    immune_data =  c(rep("Health Report", round(data[3,2]*data[3,6]/100)), rep("Mothers Report", round(data[3,3]*data[3,6]/100)), rep("No immune", round(data[3,5]*data[3,6]/100)), 
+                                 rep("Health Report", round(data[4,2]*data[4,6]/100)), rep("Mothers Report", round(data[4,3]*data[4,6]/100)), rep("No immune", round(data[4,5]*data[4,6]/100)),
+                                 rep("Health Report", round(data[5,2]*data[5,6]/100)), rep("Mothers Report", round(data[5,3]*data[5,6]/100)), rep("No immune", round(data[5,5]*data[5,6]/100)), 
+                                 rep("Health Report", round(data[6,2]*data[6,6]/100)), rep("Mothers Report", round(data[6,3]*data[6,6]/100)), rep("No immune", round(data[6,5]*data[6,6]/100)),
+                                 rep("Health Report", round(data[7,2]*data[7,6]/100)), rep("Mothers Report", round(data[7,3]*data[7,6]/100)), rep("No immune", round(data[7,5]*data[7,6]/100)))
+                    )
+
+# create new dataset only for for education
+
+ # no_edu <-data.frame(education = c(rep("no_edu", 265)),
+ #                     immune_data = c(rep("Health Report", round(data[8,2]*data[8,6]/100)), rep("Mothers Report", round(data[8,3]*data[8,6]/100)), rep("No immune", round(data[8,5]*data[8,6]/100)))
+ #                     )
+ # 
+ # primary <-data.frame(education = c(rep("primary", data[9,6])),
+ #                     immune_data = c(rep("Health Report", round(data[9,2]*data[9,6]/100)), rep("Mothers Report", floor(data[9,3]*data[9,6]/100)), rep("No immune", round(data[9,5]*data[9,6]/100)))
+ #                     )
+ # 
+ # secondary <-data.frame(education = c(rep("secondary", data[10,6])),
+ #                     immune_data = c(rep("Health Report", floor(data[10,2]*data[10,6]/100)), rep("Mothers Report", floor(data[10,3]*data[10,6]/100)), rep("No immune", round(data[10,5]*data[10,6]/100)))
+ #                    )
+# education <- data.frame(education = c(rep("no_education", data[8,6]), rep("primary", data[9,6]), rep("secondary", data[10,6]), rep("higher", data[11,6])),
+#                     immune_data =  c(rep("Health Report", round(data[8,2]*data[8,6]/100)), rep("Mothers Report", round(data[8,3]*data[8,6]/100)), rep("No immune", round(data[8,5]*data[8,6]/100)), 
+#                                  rep("Health Report", round(data[9,2]*data[9,6]/100)), rep("Mothers Report", round(data[9,3]*data[9,6]/100)), rep("No immune", round(data[9,5]*data[9,6]/100)),
+#                                  rep("Health Report", round(data[10,2]*data[10,6]/100)), rep("Mothers Report", round(data[10,3]*data[10,6]/100)), rep("No immune", round(data[10,5]*data[10,6]/100)), 
+#                                  rep("Health Report", round(data[11,2]*data[11,6]/100)), rep("Mothers Report", round(data[11,3]*data[11,6]/100)), rep("No immune", round(data[11,5]*data[11,6]/100)))
+#                     )
+
+# create new dataset only for for education
+religion <- data.frame(religion = c(rep("Buddhist", data[12,6]), rep("Islam", data[13,6])),
+                immune_data =  c(rep("Health Report", round(data[12,2]*data[12,6]/100)), rep("Mothers Report", round(data[12,3]*data[12,6]/100)), rep("No immune", round(data[12,5]*data[12,6]/100)), 
+                                 rep("Health Report", round(data[13,2]*data[13,6]/100)), rep("Mothers Report", round(data[13,3]*data[13,6]/100)), rep("No immune", round(data[13,5]*data[13,6]/100)))
+                      )
 ```
@@
 ```{r}
-data %>%
-  ggplot(aes(x = Variable, y = Health_Record)) +
-  geom_bar(stat='identity') +
-  coord_flip()
+#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
+urban_rural %>%
+  ggplot(aes(x = location, fill = immune_data)) +
+  geom_bar(position = "dodge")
 ```
-
+```{r}
+#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
+region %>%
+  ggplot(aes(x = region, fill = immune_data)) +
+  geom_bar(position = "dodge")
+```
+```{r}
+#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
+```
+```{r}
+#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
+religion %>%
+  ggplot(aes(x = religion, fill = immune_data)) +
+  geom_bar(position = "dodge")
+```
 Talk more about it.

### 2022-04-02 scripts/02-clean_and_prepare_data.R

@@ -51,7 +51,6 @@ agent <-
   interrogate()
 
 agent
-view(cleaned_data)
 
 #### Save ####
 write_csv(cleaned_data, "outputs/data/cleaned_data.csv")

### 2022-04-02 outputs/paper/paper.Rmd
ggplot

--- 2022-03-31 outputs/paper/paper.Rmd
@@
 data <- read_csv("outputs/data/cleaned_data.csv")
+
+urban_rural <- pivot_longer(data[1:2, 1:5], -Variable, names_to="immune_status", values_to="value")
+region <- pivot_longer(data[3:7, 1:5], -Variable, names_to="immune_status", values_to="value")
+education <- pivot_longer(data[8:11, 1:5], -Variable, names_to="immune_status", values_to="value")
+religion <- pivot_longer(data[12:13, 1:5], -Variable, names_to="immune_status", values_to="value")
+total <- pivot_longer(data[14, 1:5], -Variable, names_to="immune_status", values_to="value")
+population <- data.frame(Variable = data$Variable, Population = data$Number_of_Children)
+
+# create new dataset only for urban-rural data
+# urban_rural <- data.frame(location = c(rep("urban", data[1,6]), rep("rural", data[2,6])),
+#                 immune_data =  c(rep("Health Report", round(data[1,2]*data[1,6]/100)), rep("Mothers Report", round(data[1,3]*data[1,6]/100)), rep("No immune", round(data[1,5]*data[1,6]/100)), 
+#                                  rep("Health Report", round(data[2,2]*data[2,6]/100)), rep("Mothers Report", round(data[2,3]*data[2,6]/100)), rep("No immune", round(data[2,5]*data[2,6]/100)))
+#                 
+#                 )
+
+# create new dataset only for for region
+# region <- data.frame(region = c(rep("north", data[3,6]), rep("north_east", data[4,6]), rep("central", data[5,6]), rep("south", data[6,6]), rep("bangkok", data[7,6])),
+#                     immune_data =  c(rep("Health Report", round(data[3,2]*data[3,6]/100)), rep("Mothers Report", round(data[3,3]*data[3,6]/100)), rep("No immune", round(data[3,5]*data[3,6]/100)), 
+#                                  rep("Health Report", round(data[4,2]*data[4,6]/100)), rep("Mothers Report", round(data[4,3]*data[4,6]/100)), rep("No immune", round(data[4,5]*data[4,6]/100)),
+#                                  rep("Health Report", round(data[5,2]*data[5,6]/100)), rep("Mothers Report", round(data[5,3]*data[5,6]/100)), rep("No immune", round(data[5,5]*data[5,6]/100)), 
+#                                  rep("Health Report", round(data[6,2]*data[6,6]/100)), rep("Mothers Report", round(data[6,3]*data[6,6]/100)), rep("No immune", round(data[6,5]*data[6,6]/100)),
+#                                  rep("Health Report", round(data[7,2]*data[7,6]/100)), rep("Mothers Report", round(data[7,3]*data[7,6]/100)), rep("No immune", round(data[7,5]*data[7,6]/100)))
+#                     )
+
+# create new dataset only for for education. due to an error in the dataset provided by DHS, some rows will be filled with NA.
+
+ # no_edu <-data.frame(education = c(rep("no_edu", 265)),
+ #                     immune_data = c(rep("Health Report", round(data[8,2]*data[8,6]/100)), rep("Mothers Report", round(data[8,3]*data[8,6]/100)), rep("No immune", round(data[8,5]*data[8,6]/100)))
+ #                     )
+ # 
+ # primary <-data.frame(education = c(rep("primary", data[9,6])),
+ #                     immune_data = c(rep("Health Report", round(data[9,2]*data[9,6]/100)), rep("Mothers Report", floor(data[9,3]*data[9,6]/100)), rep("No immune", round(data[9,5]*data[9,6]/100)))
+ #                     )
+ # 
+ # secondary <-data.frame(education = c(rep("secondary", data[10,6])),
+ #                     immune_data = c(rep("Health Report", floor(data[10,2]*data[10,6]/100)), rep("Mothers Report", floor(data[10,3]*data[10,6]/100)), rep("No immune", round(data[10,5]*data[10,6]/100)))
+ #                    )
+# education <- data.frame(education = c(rep("no_education", round(data[8,2]*data[8,6]/100) + round(data[8,3]*data[8,6]/100) + round(data[8,5]*data[8,6]/100)), 
+#                                       rep("primary", round(data[9,2]*data[9,6]/100) + round(data[9,3]*data[9,6]/100) + round(data[9,5]*data[9,6]/100)), 
+#                                       rep("secondary", round(data[10,2]*data[10,6]/100) + round(data[10,3]*data[10,6]/100) + round(data[10,5]*data[10,6]/100)),
+#                                       rep("higher", round(data[11,2]*data[11,6]/100) + round(data[11,3]*data[11,6]/100) + round(data[11,5]*data[11,6]/100))),
+#                     immune_data =  c(rep("Health Report", round(data[8,2]*data[8,6]/100)), rep("Mothers Report", round(data[8,3]*data[8,6]/100)), rep("No immune", round(data[8,5]*data[8,6]/100)),
+#                                  rep("Health Report", round(data[9,2]*data[9,6]/100)), rep("Mothers Report", round(data[9,3]*data[9,6]/100)), rep("No immune", round(data[9,5]*data[9,6]/100)),
+#                                  rep("Health Report", round(data[10,2]*data[10,6]/100)), rep("Mothers Report", round(data[10,3]*data[10,6]/100)), rep("No immune", round(data[10,5]*data[10,6]/100)),
+#                                  rep("Health Report", round(data[11,2]*data[11,6]/100)), rep("Mothers Report", round(data[11,3]*data[11,6]/100)), rep("No immune", round(data[11,5]*data[11,6]/100)))
+#                     )
+
+# create new dataset only for for education
+# religion <- data.frame(religion = c(rep("Buddhist", data[12,6]), rep("Islam", data[13,6])),
+#                 immune_data =  c(rep("Health Report", round(data[12,2]*data[12,6]/100)), rep("Mothers Report", round(data[12,3]*data[12,6]/100)), rep("No immune", round(data[12,5]*data[12,6]/100)), 
+#                                  rep("Health Report", round(data[13,2]*data[13,6]/100)), rep("Mothers Report", round(data[13,3]*data[13,6]/100)), rep("No immune", round(data[13,5]*data[13,6]/100)))
+#                       )
+# 
+# total <- data.frame(total = c(rep("total", data[14,6])),
+#                 immune_data =  c(rep("Health Report", floor(data[14,2]*data[14,6]/100)), rep("Mothers Report", floor(data[14,3]*data[14,6]/100)), rep("No immune", floor(data[14,5]*data[14,6]/100)))
+#                       )
 ```
@@
 ```{r}
-data %>%
-  ggplot(aes(x = Variable, y = Health_Record)) +
-  geom_bar(stat='identity') +
+population %>%
+  ggplot(aes(x = Variable, y = Population, fill = Variable)) +
+  geom_bar(stat='identity', position = "dodge") +
   coord_flip()
@@
 
+```{r}
+#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
+urban_rural %>%
+  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
+  geom_bar(stat='identity', position = "dodge") +
+  coord_flip()
+```
+```{r}
+#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
+region %>%
+  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
+  geom_bar(stat='identity', position = "dodge") +
+  coord_flip()
+```
+```{r}
+#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
+education %>%
+  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
+  geom_bar(stat='identity', position = "dodge") +
+  coord_flip()
+```
+```{r}
+#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
+religion %>%
+  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
+  geom_bar(stat='identity', position = "dodge") +
+  coord_flip()
+```
 Talk more about it.
@@
 ```{r}
-
+total %>%
+  ggplot(aes(x = immune_status, y = value, fill = immune_status)) +
+  geom_bar(stat='identity', position = "dodge") +
+  coord_flip()
 ```

### 2022-04-02 outputs/paper/paper.Rmd
Title, Abstract, Data writing

--- 2022-04-02 outputs/paper/paper.Rmd
@@
 ---
-title: "Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]"
-subtitle: "Possible factors effecting 2016 election"
+title: "The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]"
+subtitle: "Why there exists gap between health system and mother's report for immunization"
 author: 
@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "This paper has been examined possible variables that influenced U.S citizens' choice for the 2016 U.S presidential election.
-We have found that there exists significantly different opinions regarding gender, wealth, race and age.
-This is important in a sesne that it shows thought trends as well as crucial decision indicators for voting in U.S.,With further survey at the end of this paper, we are going to explore whether this is happening only in U.S or not."
+abstract: "This paper has been examined possible variables that influenced children immunization report cases between healthcare system and mother's report in Thailand.
+We have found that there exists significant difference regarding communities, region, education level and religion.
+This is important in a sense that it relates to lives as well as indication for why such gap exits.
+We will discuss the importance in details at discussion session."
 output:
@@
 
-You can and should cross-reference sections and sub-sections.
-For instance, Section \@ref(data).
-R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point).
+The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; and 6) why it is important.
+A reader should be able to read only the introduction and have a good idea about the research that was carried out.
 
 # Data
+To obtain data with respect to our interest, we took an approach to Thailand DHS survey in 1980s and 1990s.
+Among many candidates, we chose year 1987.
+In the survey, there existed many data similar to our aim.
+For instance, a data presented child and infant mortality with respect to participants' features.
+It showed the mortality rate with same variables that our data has.
+However, we thought that mortality alone could not be enough to show the gap existed between healthcare system and mothers.
+Following that, we made a decision that combining other variables would cause bias in this research.
+The data we chose presents cases of children immunization status between communities(urban and rural), region(north,northeast,central,south and Bangkok), education level(no education, primary, secondary and higher), religion: (Buddhist and Islam), and whether they were reported from healthcare or mother, or their children did not get one or not.
+For a small drawback, other religions such as Christianity was excluded since majority of Thai believed Buddhism and almost rest believed Islam.
+Now let's begin to talk about our data in details.
+
+1) Communities
+- Urban
+- Rural
+
+Surprisingly, in 1987 Thailand, if you take a look at figure\@ref(fig:fig1), there were more people in rural  than urban areas.
+According to Statistic, urbanization rate in Thailand from 2010 to 2020  slowly increased but it still remained mid 40 percentage to 50 percentage.
+This is very small compared to that of US, which is mid 70 to 80.
+In addition to the population density between urban and rural, mother's report cases were extremely more than healthcare in rural area.
+Calculating the percentage, it was 60 and 22.8 percentage.
+On the other hand, there seems comparatively similar cases from healthcare and mothers in urban areas.
+Lastly,immunization rate is higher in urban compared to rural areas.
+
+2) Region
+- North
+- Northeast
+- Central
+- South
+- Bangkok
+
+As we have observed in figure\@ref(fig:fig1), figure\@ref(fig:fig2) shows regional based immunization status.
+Most participants were not from Bangkok, the capital of Thailand.
+Instead, they were from Northeast.
+This is because Islan, the northeast part of Thailand, is the largest region of Thailand, and urbanization in Thailand is relatively low.
+The graph shows very similar trends observed in \@ref(fig:fig1).
+There were more mother's reports outside of Bangkok, and less immunization rate outside of Bangkok.
+One thing to notice is that percentage of mother's reports in Northeast is noticeably higher.
+
+3) Education level
+- No Education
+- Primary
+- Secondary
+- Higher
+
+4) Religion
+- Buddhist
+- Islam
+
+We have discussed about small drawback in religion, which is other religion except Buddhisms and Islam were not collected.
+Further, majority of Thai people believes in Buddhism, thus in the graph figure\@ref(fig:fig4), you can observe that there existed more cases in Buddhism than Islam.
+As we observed up to this point, similar to other variables, there existed more mother's report cases than that of healthcare with no exception to religion.
 ```{r, include=FALSE, echo=FALSE}
@@
 
-```{r}
+```{r fig1,echo=FALSE, fig.cap = "Immunization cases between communities"}
 #ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
@@
 ```
-```{r}
+
+```{r fig2,echo=FALSE, fig.cap = "Immunization cases between region"}
 #ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
@@
 ```
-```{r}
+
+```{r fig4,echo=FALSE, fig.cap = "Immunization cases between religion"}
 #ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
@@
 ```
-Talk more about it.
-
-Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)
 
@@
 
-Talk way more about it.
-
-# Model
+# Results
 
@@
 # References
+https://www.statista.com/statistics/455942/urbanization-in-thailand/
+https://www.statista.com/statistics/269967/urbanization-in-the-united-states/

### 2022-04-02 outputs/paper/paper.Rmd
update ggplot

--- 2022-04-02 outputs/paper/paper.Rmd
@@
 region %>%
-  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
+  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
   geom_bar(stat='identity', position = "dodge") +
@@
 education %>%
-  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
+  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
   geom_bar(stat='identity', position = "dodge") +

### 2022-04-02 outputs/paper/paper.Rmd
ggplot

--- 2022-04-02 outputs/paper/paper.Rmd
@@
 
-urban_rural <- pivot_longer(data[1:2, 1:5], -Variable, names_to="immune_status", values_to="value")
-region <- pivot_longer(data[3:7, 1:5], -Variable, names_to="immune_status", values_to="value")
-education <- pivot_longer(data[8:11, 1:5], -Variable, names_to="immune_status", values_to="value")
-religion <- pivot_longer(data[12:13, 1:5], -Variable, names_to="immune_status", values_to="value")
-total <- pivot_longer(data[14, 1:5], -Variable, names_to="immune_status", values_to="value")
-population <- data.frame(Variable = data$Variable, Population = data$Number_of_Children)
+urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+population <- data.frame(Variable = data$Variable, 
+                         Population = data$Number_of_Children) %>% head(-1)
+population$Variable <- factor(population$Variable,
+                              levels = population$Variable) %>% fct_rev()
+```
+```{r}
 

### 2022-04-02 outputs/paper/paper.Rmd
update ggplot

--- 2022-04-02 outputs/paper/paper.Rmd
@@
 
-urban_rural <- pivot_longer(data[1:2, 1:5], -Variable, names_to="immune_status", values_to="value")
-region <- pivot_longer(data[3:7, 1:5], -Variable, names_to="immune_status", values_to="value")
-education <- pivot_longer(data[8:11, 1:5], -Variable, names_to="immune_status", values_to="value")
-religion <- pivot_longer(data[12:13, 1:5], -Variable, names_to="immune_status", values_to="value")
-total <- pivot_longer(data[14, 1:5], -Variable, names_to="immune_status", values_to="value")
+urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
 population <- data.frame(Variable = data$Variable, Population = data$Number_of_Children)

### 2022-04-02 outputs/paper/paper.Rmd

@@
 total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
-population <- data.frame(Variable = data$Variable, Population = data$Number_of_Children)
+population <- data.frame(Variable = data$Variable, 
+                         Population = data$Number_of_Children) %>% head(-1)
+population$Variable <- factor(population$Variable,
+                              levels = population$Variable) %>% fct_rev()
+```
+
+```{r}
 

### 2022-04-02 outputs/paper/paper.Rmd
Introduction writing

--- 2022-04-02 outputs/paper/paper.Rmd
@@
 
-You can and should cross-reference sections and sub-sections.
-For instance, Section \@ref(data).
-R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point).
+The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; and 6) why it is important.
+A reader should be able to read only the introduction and have a good idea about the research that was carried out.
+
+Trust is a big matter in this world.
+Especially when you need assistance from areas that you are unfamiliar with, trust is the best thing that you can rely on.
+For instance, if you need a lawyer, the best thing that you can do is trust him/her/the, and be 100% honest to your lawyer.
+In medical field, trust directly relates to your life.
+We are certain that you have observed that many people have been refusing to get vaccine for COVID-19.
+Then, we start to wonder whether the COVID-19 vaccine controversy is similar to other vaccines that are proved and guaranteed safety such as BCG vaccine for preventing tuberculosis.
+It is true that we no longer have doubts against them.
+However, we thought that if you move sight to developing country in 1980~1990s, situation would certainly different because of well constructed healthcare system or other reasons.
+This curiosty triggered us to start this research.
+
+This paper is about children immunization reports in 1987 Thailand.
+Specifically how the rate differs between communities, regions, people with different education levels and religion.
+Along with that, its cases are divided into reports from mothers and healthcare.
+There clearly exists limitations and gaps that we need to fill.
+First, we are now in 2022.
+We cannot go back to the period and conduct research regarding our focus.
+Second, thoughts cannot be measured thoroughly.
 
 # Data
+To obtain data with respect to our interest, we took an approach to Thailand DHS survey in 1980s and 1990s.
+Among many candidates, we chose year 1987.
+In the survey, there existed many data similar to our aim.
+For instance, a data presented child and infant mortality with respect to participants' features.
+It showed the mortality rate with same variables that our data has.
+However, we thought that mortality alone could not be enough to show the gap existed between healthcare system and mothers.
+Following that, we made a decision that combining other variables would cause bias in this research.
+The data we chose presents cases of children immunization status between communities(urban and rural), region(north,northeast,central,south and Bangkok), education level(no education, primary, secondary and higher), religion: (Buddhist and Islam), and whether they were reported from healthcare or mother, or their children did not get one or not.
+For a small drawback, other religions such as Christianity was excluded since majority of Thai believed Buddhism and almost rest believed Islam.
+Now let's begin to talk about our data in details.
+
+1) Communities
+- Urban
+- Rural
+
+Surprisingly, in 1987 Thailand, if you take a look at figure\@ref(fig:fig1), there were more people in rural  than urban areas.
+According to Statistic, urbanization rate in Thailand from 2010 to 2020  slowly increased but it still remained mid 40 percentage to 50 percentage.
+This is very small compared to that of US, which is mid 70 to 80.
+In addition to the population density between urban and rural, mother's report cases were extremely more than healthcare in rural area.
+Calculating the percentage, it was 60 and 22.8 percentage.
+On the other hand, there seems comparatively similar cases from healthcare and mothers in urban areas.
+Lastly,immunization rate is higher in urban compared to rural areas.
+
+2) Region
+- North
+- Northeast
+- Central
+- South
+- Bangkok
+
+As we have observed in figure\@ref(fig:fig1), figure\@ref(fig:fig2) shows regional based immunization status.
+Most participants were not from Bangkok, the capital of Thailand.
+Instead, they were from Northeast.
+This is because Islan, the northeast part of Thailand, is the largest region of Thailand, and urbanization in Thailand is relatively low.
+The graph shows very similar trends observed in \@ref(fig:fig1).
+There were more mother's reports outside of Bangkok, and less immunization rate outside of Bangkok.
+One thing to notice is that percentage of mother's reports in Northeast is noticeably higher.
+
+3) Education level
+- No Education
+- Primary
+- Secondary
+- Higher
+
+If you look at figure\@ref(fig:fig4), you can observe that as education level goes up, gap between mother's report and healthcare is being equalized.
+In addition to that, non immunization rate decreases.
+One thing to notice is that higher education you have in Thailand there existed more immunization rate.
+For instance, people with higher education shows immunization rate close to 100%.
+
+4) Religion
+- Buddhist
+- Islam
+
+We have discussed about small drawback in religion, which is other religion except Buddhisms and Islam were not collected.
+Further, majority of Thai people believes in Buddhism, thus in the graph figure\@ref(fig:fig4), you can observe that there existed more cases in Buddhism than Islam.
+As we observed up to this point, similar to other variables, there existed more mother's report cases than that of healthcare with no exception to religion.
 ```{r, include=FALSE, echo=FALSE}
@@
 
-urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
-region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
-education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
-religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
-total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+urban_rural <- pivot_longer(data[1:2, 1:5], -Variable, names_to="immune_status", values_to="value")
+region <- pivot_longer(data[3:7, 1:5], -Variable, names_to="immune_status", values_to="value")
+education <- pivot_longer(data[8:11, 1:5], -Variable, names_to="immune_status", values_to="value")
+religion <- pivot_longer(data[12:13, 1:5], -Variable, names_to="immune_status", values_to="value")
+total <- pivot_longer(data[14, 1:5], -Variable, names_to="immune_status", values_to="value")
 population <- data.frame(Variable = data$Variable, Population = data$Number_of_Children)
@@
 
-```{r}
+```{r fig1,echo=FALSE, fig.cap = "Immunization cases between communities"}
 population %>%
@@
 
-```{r}
+```{r fig2,echo=FALSE, fig.cap = "Immunization cases between communities"}
 #ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
@@
 ```
-```{r}
+
+```{r fig3,echo=FALSE, fig.cap = "Immunization cases between region"}
 #ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
@@
 ```
-```{r}
+```{r fig4,echo=FALSE, fig.cap = "Immunization cases between education"}
 #ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
@@
 ```
-```{r}
+
+```{r fig5,echo=FALSE, fig.cap = "Immunization cases between religion"}
 #ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
@@
 ```
-Talk more about it.
 
-Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)
-
-```{r}
+```{r fig6,echo=FALSE, fig.cap = "Immunization and non-immunization cases total"}
 total %>%

### 2022-04-02 outputs/paper/paper.Rmd

@@
 
-urban_rural <- pivot_longer(data[1:2, 1:5], -Variable, names_to="immune_status", values_to="value")
-region <- pivot_longer(data[3:7, 1:5], -Variable, names_to="immune_status", values_to="value")
-education <- pivot_longer(data[8:11, 1:5], -Variable, names_to="immune_status", values_to="value")
-religion <- pivot_longer(data[12:13, 1:5], -Variable, names_to="immune_status", values_to="value")
-total <- pivot_longer(data[14, 1:5], -Variable, names_to="immune_status", values_to="value")
-population <- data.frame(Variable = data$Variable, Population = data$Number_of_Children)
+urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+population <- data.frame(Variable = data$Variable, 
+                         Population = data$Number_of_Children) %>% head(-1)
+population$Variable <- factor(population$Variable,
+                              levels = population$Variable) %>% fct_rev()
+```
+
+```{r}
 

### 2022-04-02 outputs/paper/paper.Rmd
ggplot titles

--- 2022-04-02 outputs/paper/paper.Rmd
@@
   geom_bar(stat='identity', position = "dodge") +
-  coord_flip()
+  coord_flip()  +
+  labs(x = element_blank(),
+       y = "Percent",
+       title = "Percentage of Children's Immunization Status",
+       )
 ```
@@
   geom_bar(stat='identity', position = "dodge") +
-  coord_flip()
+  coord_flip() +
+  labs(x = element_blank(),
+       y = "Percent",
+       title = "Percentage of Children's Immunization Status",
+       ) +
+  theme(legend.position = "none")
 ```

### 2022-04-02 outputs/paper/paper.Rmd
Introduction writing started

--- 2022-04-02 outputs/paper/paper.Rmd
@@
 # Introduction
-
-The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; and 6) why it is important.
-A reader should be able to read only the introduction and have a good idea about the research that was carried out.
-
 Trust is a big matter in this world.
@@
 Second, thoughts cannot be measured thoroughly.
+To overcome the limitations, we tried to look for powerful candidates.
+Among many, we thought that 1987 DHS survey in Thailand specifically regarding children immunization rate with respect to healthcare, their mothers and the participants' features would be the best one to represent our interest.
+
+We first had to convert pdf file to csv.After that throughout the analysis of relation between the variables and immunization rate reported by healthcare and mothers, we could observe that there existed significant gap between healthcare and mothers with respect to variables.
+This is an important finding because it shows that there could be lack of trust toward healthcare system or shortage of healthcare supports in Thailand.
+With further research after, we can observe how it has been improved since 1987, but for now we are going to focus on why.
+For detailed answer for why will be discussed in discussion session.
+
+For this paper, after this introduction session, you are going to explore
+
+2) Data
+3) Results
+4) Discussion
+5) Reference list
 

### 2022-04-02 outputs/paper/paper.Rmd
Abstract, Introduction, Data session writing edited

@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "This paper has been examined possible variables that influenced children immunization report cases between healthcare system and mother's report in Thailand.
-We have found that there exists significant difference regarding communities, region, education level and religion.
-This is important in a sense that it relates to lives as well as indication for why such gap exits.
-We will discuss the importance in details at discussion session."
+abstract: "This paper has been examined possible variables that influenced children immunization report cases between healthcare system and mother's reports in Thailand.
+We have found that there existed significantly different rate regarding communities, region, education level and religion.
+This is important in a sense that it relates to lives as well as indication for why such gap exited.
+We will discuss its importance in details later in discussion session."
 output:
@@
 Trust is a big matter in this world.
-Especially when you need assistance from areas that you are unfamiliar with, trust is the best thing that you can rely on.
-For instance, if you need a lawyer, the best thing that you can do is trust him/her/the, and be 100% honest to your lawyer.
-In medical field, trust directly relates to your life.
-We are certain that you have observed that many people have been refusing to get vaccine for COVID-19.
-Then, we start to wonder whether the COVID-19 vaccine controversy is similar to other vaccines that are proved and guaranteed safety such as BCG vaccine for preventing tuberculosis.
+Especially when you need assistance in fields that you are unfamiliar with, trust is the best thing that you can rely on.
+For instance, if you need a lawyer, the best thing that you can do is to trust your lawyer, and be 100% honest.
+In medical field, trust is directly related to your life.
+We are certain that you have observed that many people have been refusing to get COVID-19 vaccines.
+Then, we started to wonder whether the COVID-19 vaccine controversy is similar to other vaccines that safety are proved and guaranteed such as BCG vaccine for preventing tuberculosis.
 It is true that we no longer have doubts against them.
-However, we thought that if you move sight to developing country in 1980~1990s, situation would certainly different because of well constructed healthcare system or other reasons.
-This curiosty triggered us to start this research.
+However, if you move sight to developing country in 1980~1990s, situation would certainly different because of lack of well constructed healthcare system or other reasons.
+This curiosity triggered us to start this research.
 
-This paper is about children immunization reports in 1987 Thailand.
+This paper is about children immunization reports in 1987, Thailand.
 Specifically how the rate differs between communities, regions, people with different education levels and religion.
 Along with that, its cases are divided into reports from mothers and healthcare.
-There clearly exists limitations and gaps that we need to fill.
-First, we are now in 2022.
+There clearly exists limitations and gaps that we are required to fill.
+First, gap between present and past.
 We cannot go back to the period and conduct research regarding our focus.
@@
 To overcome the limitations, we tried to look for powerful candidates.
-Among many, we thought that 1987 DHS survey in Thailand specifically regarding children immunization rate with respect to healthcare, their mothers and the participants' features would be the best one to represent our interest.
+Among many, we thought that 1987 DHS survey in Thailand specifically regarding children immunization rate from healthcare and mothers with respect to their features would be the best one to represent our interest.
 
-We first had to convert pdf file to csv.After that throughout the analysis of relation between the variables and immunization rate reported by healthcare and mothers, we could observe that there existed significant gap between healthcare and mothers with respect to variables.
+Dataset was not open.
+Instead, the survey presented various tables.
+Thus, we were required to convert pdf file to csv.
+After that throughout the analysis of relation between the variables and immunization rate reported by healthcare and mothers, we could observe that there existed significant gap between healthcare and mothers with respect to variables.
 This is an important finding because it shows that there could be lack of trust toward healthcare system or shortage of healthcare supports in Thailand.
-With further research after, we can observe how it has been improved since 1987, but for now we are going to focus on why.
+Thus, it can indicate where or who to focus for the healthcare system to gain trust.
+With further research, we will be able observe how it has been improved since 1987, but for now we are going to focus on why the gap existed in 1987, Thailand.
 For detailed answer for why will be discussed in discussion session.
@@
 Among many candidates, we chose year 1987.
-In the survey, there existed many data similar to our aim.
+In the survey, there existed many similar data regarding our aim.
 For instance, a data presented child and infant mortality with respect to participants' features.
 It showed the mortality rate with same variables that our data has.
-However, we thought that mortality alone could not be enough to show the gap existed between healthcare system and mothers.
+However, we thought that mortality alone could not be enough to show why the gap existed between healthcare system and mothers.
 Following that, we made a decision that combining other variables would cause bias in this research.
-The data we chose presents cases of children immunization status between communities(urban and rural), region(north,northeast,central,south and Bangkok), education level(no education, primary, secondary and higher), religion: (Buddhist and Islam), and whether they were reported from healthcare or mother, or their children did not get one or not.
-For a small drawback, other religions such as Christianity was excluded since majority of Thai believed Buddhism and almost rest believed Islam.
+The data we chose presented cases of children immunization status between communities(urban and rural), region(north,northeast,central,south and Bangkok), education level(no education, primary, secondary and higher), religion: (Buddhist and Islam), and where they were reported, or whether  children did not get one or not.
+For a small drawback, other religions such as Christianity was excluded since majority of Thai believe in Buddhism and rest believe in Islam.
 Now let's begin to talk about our data in details.
@@
 This is very small compared to that of US, which is mid 70 to 80.
-In addition to the population density between urban and rural, mother's report cases were extremely more than healthcare in rural area.
-Calculating the percentage, it was 60 and 22.8 percentage.
-On the other hand, there seems comparatively similar cases from healthcare and mothers in urban areas.
+In addition to the population density between urban and rural, mother's report cases were more than healthcare in rural area.
+Calculating the percentage, it was 60% vs 22.8%.
+On the other hand, there seems comparatively similar cases between healthcare and mothers in urban areas.
 Lastly,immunization rate is higher in urban compared to rural areas.
@@
 
-As we have observed in figure\@ref(fig:fig1), figure\@ref(fig:fig2) shows regional based immunization status.
+Figure\@ref(fig:fig2) shows regional based immunization status.
 Most participants were not from Bangkok, the capital of Thailand.
@@
 This is because Islan, the northeast part of Thailand, is the largest region of Thailand, and urbanization in Thailand is relatively low.
-The graph shows very similar trends observed in \@ref(fig:fig1).
+The graph shows very similar trends with \@ref(fig:fig1).
 There were more mother's reports outside of Bangkok, and less immunization rate outside of Bangkok.
+On the other hand, comparatively equal cases are observed in Bangkok.
 One thing to notice is that percentage of mother's reports in Northeast is noticeably higher.
@@
 
-If you look at figure\@ref(fig:fig4), you can observe that as education level goes up, gap between mother's report and healthcare is being equalized.
+If you look at figure\@ref(fig:fig4), you can observe that as education level goes up, gap between mother's report and healthcare is being filled.
 In addition to that, non immunization rate decreases.
-One thing to notice is that higher education you have in Thailand there existed more immunization rate.
+One thing to notice is that higher education you have in Thailand, there existed more immunization rate.
 For instance, people with higher education shows immunization rate close to 100%.
@@
 
-We have discussed about small drawback in religion, which is other religion except Buddhisms and Islam were not collected.
-Further, majority of Thai people believes in Buddhism, thus in the graph figure\@ref(fig:fig4), you can observe that there existed more cases in Buddhism than Islam.
-As we observed up to this point, similar to other variables, there existed more mother's report cases than that of healthcare with no exception to religion.
+At the beginning of introduction, we talked about small drawback in religion, which is other religions except Buddhisms and Islam were not collected.
+Moreover, majority of Thai people believes in Buddhism, thus in the graph figure\@ref(fig:fig4), you can observe that there existed more cases in Buddhism than Islam.
+As we have observed up to this point, similar to other variables, there existed more mother's report cases than that of healthcare with no exception to religion.
+
 ```{r, include=FALSE, echo=FALSE}

### 2022-04-02 outputs/paper/paper.Rmd
Figure edited

@@
 At the beginning of introduction, we talked about small drawback in religion, which is other religions except Buddhisms and Islam were not collected.
-Moreover, majority of Thai people believes in Buddhism, thus in the graph figure\@ref(fig:fig4), you can observe that there existed more cases in Buddhism than Islam.
+Moreover, majority of Thai people believes in Buddhism \@ref(fig:fig1), thus in the graph figure\@ref(fig:fig4), you can observe that there existed more cases in Buddhism than Islam.
 As we have observed up to this point, similar to other variables, there existed more mother's report cases than that of healthcare with no exception to religion.

### 2022-04-02 outputs/paper/paper.Rmd
results session writing started

--- 2022-04-02 outputs/paper/paper.Rmd
@@
 
-Surprisingly, in 1987 Thailand, if you take a look at figure\@ref(fig:fig1), there were more people in rural than urban areas.
+Surprisingly, in 1987 Thailand, if you take a look at figure\@ref(fig:fig1) and \@ref(fig:fig2), there were more people in rural than urban areas.
 According to Statistic, urbanization rate in Thailand from 2010 to 2020  slowly increased but it still remained mid 40 percentage to 50 percentage.
@@
 
-Figure\@ref(fig:fig2) shows regional based immunization status.
+Figure\@ref(fig:fig3) shows regional based immunization status.
 Most participants were not from Bangkok, the capital of Thailand.
@@
 At the beginning of introduction, we talked about small drawback in religion, which is other religions except Buddhisms and Islam were not collected.
-Moreover, majority of Thai people believes in Buddhism, thus in the graph figure\@ref(fig:fig4), you can observe that there existed more cases in Buddhism than Islam.
+Moreover, majority of Thai people believes in Buddhism \@ref(fig:fig1), thus in the graph figure\@ref(fig:fig5), you can observe that there existed more cases in Buddhism than Islam.
 As we have observed up to this point, similar to other variables, there existed more mother's report cases than that of healthcare with no exception to religion.
@@
 
-```{r fig1,echo=FALSE, fig.cap = "Immunization cases between communities"}
+```{r fig1,echo=FALSE, fig.cap = "Immunization cases between variables"}
 population %>%
@@
 # Results
+Results will likely require summary statistics, tables, graphs, images, and possibly statistical analysis or maps.
+To be clear, you should also have text associated with all these aspects.
+Show the reader the results by plotting them.
+Talk about them.
+Explain them.
+That said, this section should strictly relay results.
 
-\begin{equation}
-Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
-\end{equation}
-
-Equation \@ref(eq:bayes) seems useful, eh?
-
-Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR].
-We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results
+In this session, we are going to explore the results of analysis.
+To do that, we are going to use top-down method.
+Let's take a look at figure\@ref(fig:fig6), which is the total result of immunization reports.
+This graph shows that how different immunization rate between healthcare and mother reports are with non immunization rate among 2872 participants.
 

### 2022-04-02 outputs/paper/paper.Rmd
ggplot

--- 2022-04-02 outputs/paper/paper.Rmd
@@
 5) Reference list
+
+This report was created using `R` [@citeR] and its libraries `tidyverse` [@tidyverse], `dplyr` [@dplyr], were used to process and clean the data, and `ggplot` [@ggplot] `bookdown` [@bookdown] and `knitr` [@knitr] was used to format this report.
 
@@
 total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
-population <- data.frame(Variable = data$Variable, 
+population <- data.frame(group = c(rep("urban-rural", 2), rep("region", 5), rep("education", 4), rep("religion", 3)),
+                                           Variable = data$Variable, 
                          Population = data$Number_of_Children) %>% head(-1)
@@
 
-```{r}
-
-# create new dataset only for urban-rural data
-# urban_rural <- data.frame(location = c(rep("urban", data[1,6]), rep("rural", data[2,6])),
-#                 immune_data =  c(rep("Health Report", round(data[1,2]*data[1,6]/100)), rep("Mothers Report", round(data[1,3]*data[1,6]/100)), rep("No immune", round(data[1,5]*data[1,6]/100)), 
-#                                  rep("Health Report", round(data[2,2]*data[2,6]/100)), rep("Mothers Report", round(data[2,3]*data[2,6]/100)), rep("No immune", round(data[2,5]*data[2,6]/100)))
-#                 
-#                 )
-
-# create new dataset only for for region
-# region <- data.frame(region = c(rep("north", data[3,6]), rep("north_east", data[4,6]), rep("central", data[5,6]), rep("south", data[6,6]), rep("bangkok", data[7,6])),
-#                     immune_data =  c(rep("Health Report", round(data[3,2]*data[3,6]/100)), rep("Mothers Report", round(data[3,3]*data[3,6]/100)), rep("No immune", round(data[3,5]*data[3,6]/100)), 
-#                                  rep("Health Report", round(data[4,2]*data[4,6]/100)), rep("Mothers Report", round(data[4,3]*data[4,6]/100)), rep("No immune", round(data[4,5]*data[4,6]/100)),
-#                                  rep("Health Report", round(data[5,2]*data[5,6]/100)), rep("Mothers Report", round(data[5,3]*data[5,6]/100)), rep("No immune", round(data[5,5]*data[5,6]/100)), 
-#                                  rep("Health Report", round(data[6,2]*data[6,6]/100)), rep("Mothers Report", round(data[6,3]*data[6,6]/100)), rep("No immune", round(data[6,5]*data[6,6]/100)),
-#                                  rep("Health Report", round(data[7,2]*data[7,6]/100)), rep("Mothers Report", round(data[7,3]*data[7,6]/100)), rep("No immune", round(data[7,5]*data[7,6]/100)))
-#                     )
-
-# create new dataset only for for education. due to an error in the dataset provided by DHS, some rows will be filled with NA.
-
- # no_edu <-data.frame(education = c(rep("no_edu", 265)),
- #                     immune_data = c(rep("Health Report", round(data[8,2]*data[8,6]/100)), rep("Mothers Report", round(data[8,3]*data[8,6]/100)), rep("No immune", round(data[8,5]*data[8,6]/100)))
- #                     )
- # 
- # primary <-data.frame(education = c(rep("primary", data[9,6])),
- #                     immune_data = c(rep("Health Report", round(data[9,2]*data[9,6]/100)), rep("Mothers Report", floor(data[9,3]*data[9,6]/100)), rep("No immune", round(data[9,5]*data[9,6]/100)))
- #                     )
- # 
- # secondary <-data.frame(education = c(rep("secondary", data[10,6])),
- #                     immune_data = c(rep("Health Report", floor(data[10,2]*data[10,6]/100)), rep("Mothers Report", floor(data[10,3]*data[10,6]/100)), rep("No immune", round(data[10,5]*data[10,6]/100)))
- #                    )
-# education <- data.frame(education = c(rep("no_education", round(data[8,2]*data[8,6]/100) + round(data[8,3]*data[8,6]/100) + round(data[8,5]*data[8,6]/100)), 
-#                                       rep("primary", round(data[9,2]*data[9,6]/100) + round(data[9,3]*data[9,6]/100) + round(data[9,5]*data[9,6]/100)), 
-#                                       rep("secondary", round(data[10,2]*data[10,6]/100) + round(data[10,3]*data[10,6]/100) + round(data[10,5]*data[10,6]/100)),
-#                                       rep("higher", round(data[11,2]*data[11,6]/100) + round(data[11,3]*data[11,6]/100) + round(data[11,5]*data[11,6]/100))),
-#                     immune_data =  c(rep("Health Report", round(data[8,2]*data[8,6]/100)), rep("Mothers Report", round(data[8,3]*data[8,6]/100)), rep("No immune", round(data[8,5]*data[8,6]/100)),
-#                                  rep("Health Report", round(data[9,2]*data[9,6]/100)), rep("Mothers Report", round(data[9,3]*data[9,6]/100)), rep("No immune", round(data[9,5]*data[9,6]/100)),
-#                                  rep("Health Report", round(data[10,2]*data[10,6]/100)), rep("Mothers Report", round(data[10,3]*data[10,6]/100)), rep("No immune", round(data[10,5]*data[10,6]/100)),
-#                                  rep("Health Report", round(data[11,2]*data[11,6]/100)), rep("Mothers Report", round(data[11,3]*data[11,6]/100)), rep("No immune", round(data[11,5]*data[11,6]/100)))
-#                     )
-
-# create new dataset only for for education
-# religion <- data.frame(religion = c(rep("Buddhist", data[12,6]), rep("Islam", data[13,6])),
-#                 immune_data =  c(rep("Health Report", round(data[12,2]*data[12,6]/100)), rep("Mothers Report", round(data[12,3]*data[12,6]/100)), rep("No immune", round(data[12,5]*data[12,6]/100)), 
-#                                  rep("Health Report", round(data[13,2]*data[13,6]/100)), rep("Mothers Report", round(data[13,3]*data[13,6]/100)), rep("No immune", round(data[13,5]*data[13,6]/100)))
-#                       )
-# 
-# total <- data.frame(total = c(rep("total", data[14,6])),
-#                 immune_data =  c(rep("Health Report", floor(data[14,2]*data[14,6]/100)), rep("Mothers Report", floor(data[14,3]*data[14,6]/100)), rep("No immune", floor(data[14,5]*data[14,6]/100)))
-#                       )
-```
-
-```{r fig1,echo=FALSE, fig.cap = "Immunization cases between variables"}
+```{r fig1,echo=FALSE, fig.cap = "Number of children by category"}
 population %>%
-  ggplot(aes(x = Variable, y = Population, fill = Variable)) +
+  ggplot(aes(x = Variable, y = Population, fill = group)) +
   geom_bar(stat='identity', position = "dodge") +
-  coord_flip()
+  coord_flip()  +
+  labs(x = element_blank(),
+       y = "Population",
+       title = "Distribution of Population of Children by Category",
+       ) +
+  facet_grid(group ~ ., scales="free", space="free", switch="y") +
+  theme(legend.title = element_blank()) +
+  theme(legend.position = "none")
 ```
@@
   geom_bar(stat='identity', position = "dodge") +
-  coord_flip()
+  coord_flip()  +
+  labs(x = element_blank(),
+       y = "Percent",
+       title = "Percentage of Children's Immunization Status by Urban-Rural Area",
+       ) +
+  theme(legend.title = element_blank())
 ```
@@
   geom_bar(stat='identity', position = "dodge") +
-  coord_flip()
+  coord_flip()  +
+  labs(x = element_blank(),
+       y = "Percent",
+       title = "Percentage of Children's Immunization Status by Region",
+       ) +
+  theme(legend.title = element_blank())
 ```
@@
   geom_bar(stat='identity', position = "dodge") +
-  coord_flip()
+  coord_flip()  +
+  labs(x = element_blank(),
+       y = "Percent",
+       title = "Percentage of Children's Immunization Status by Education",
+       ) +
+  theme(legend.title = element_blank())
 ```
@@
   geom_bar(stat='identity', position = "dodge") +
-  coord_flip()
+  coord_flip()  +
+  labs(x = element_blank(),
+       y = "Percent",
+       title = "Percentage of Children's Immunization Status by Religion",
+       ) +
+  theme(legend.title = element_blank())
 ```
@@
   geom_bar(stat='identity', position = "dodge") +
-  coord_flip()
+  coord_flip() +
+  labs(x = element_blank(),
+       y = "Percent",
+       title = "Total Percentage of Children's Immunization Status",
+       ) +
+  theme(legend.position = "none")
 ```

### 2022-04-03 outputs/paper/paper.Rmd
rename variables

@@
 
-urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
-region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
-education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
-religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
-total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
+# Separate the dataset by category and lengthen the dataset by moving a column to row for easier plotting.
+urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value") %>%
+  mutate(immune_status = recode(immune_status, Health_Record = "Health Record", Mothers_Report = "Mother's Report", Not_Received_Immunization = "No Immunization"))
+region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value") %>%
+  mutate(immune_status = recode(immune_status, Health_Record = "Health Record", Mothers_Report = "Mother's Report", Not_Received_Immunization = "No Immunization"))
+education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value") %>%
+  mutate(immune_status = recode(immune_status, Health_Record = "Health Record", Mothers_Report = "Mother's Report", Not_Received_Immunization = "No Immunization"))
+religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value") %>%
+  mutate(immune_status = recode(immune_status, Health_Record = "Health Record", Mothers_Report = "Mother's Report", Not_Received_Immunization = "No Immunization"))
+total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value") %>%
+  mutate(immune_status = recode(immune_status, Health_Record = "Health Record", Mothers_Report = "Mother's Report", Not_Received_Immunization = "No Immunization"))
 population <- data.frame(group = c(rep("urban-rural", 2), rep("region", 5), rep("education", 4), rep("religion", 3)),

### 2022-04-03 outputs/paper/paper.Rmd
Results session writing started

@@
 
-In this session, we are going to explore the results of analysis.
-To do that, we are going to use top-down method.
+In this session, we are going to explore the results from data analysis.
 Let's take a look at figure\@ref(fig:fig6), which is the total result of immunization reports.
-This graph shows that how different immunization rate between healthcare and mother reports are with non immunization rate among 2872 participants.
+This graph shows that how different immunization rate between healthcare and mother reports are among 2872 participants.
+58.9 percentage of immunization was reported by mothers, approximately 1691 people, 26.0 percentage for healthcare, approximately 747 people and finally 15.1 percentage for non-immunization which is approximately 434 people.
+With this numbers in mind, we are going to analyze why this phenomena occurred in Thailand with two focuses; the gap between healthcare records and mother's reports and non-immunization rate.
+First, let's take a look at figure\@ref(fig:fig2).
+From this graph, we can observe that there is not much difference in mother's reports between rural and urban areas.
+However, there is significant gap in healthcare records.
+Percentage of healthcare records for urban is 41.5% and for rural is 22.8%.
+Following that, non immunization rate in rural areas is 17.2% which is more than 3 times of non immunization rate in urban, 5.3%.
+This two gaps indicate that there needs more healthcare facilitates.
+In addition to that, percentage of mother's reports in rural areas is not
+low. This shows that there existed accessibility to vaccines in rural areas. Thus, we also conclude that lack of trust toward healthcare system could potentially affect the gap as well.
+
+Second, from figure\@ref(fig:fig3), regional based immunization rate seems very similar trends with communities.
+All over the regions, there are more mother's reports than healthcare records.
+For some specific region such as South, Northeast and Central, the gap is wider than the other two.
 

### 2022-04-04 outputs/paper/paper.Rmd
result session draft finished

@@
 58.9 percentage of immunization was reported by mothers, approximately 1691 people, 26.0 percentage for healthcare, approximately 747 people and finally 15.1 percentage for non-immunization which is approximately 434 people.
-With this numbers in mind, we are going to analyze why this phenomena occurred in Thailand with two focuses; the gap between healthcare records and mother's reports and non-immunization rate.
+With this numbers in mind, we are going to analyze why this phenomena occurred in Thailand with two focuses; the gap between healthcare records and mother's reports and non-immunization rate
+
 First, let's take a look at figure\@ref(fig:fig2).
@@
 
-Second, from figure\@ref(fig:fig3), regional based immunization rate seems very similar trends with communities.
+Second, from figure\@ref(fig:fig3), regional based immunization rate shows very similar trends with that of communities.
 All over the regions, there are more mother's reports than healthcare records.
 For some specific region such as South, Northeast and Central, the gap is wider than the other two.
+Even there were more participants who answered non-immunization than health reports in south.
+One thing to notice from this graph is North part.
+Northern Thailand shows very similar trend with Bangkok unlike other regions.
+We suspect the existence of city, Chiang Mai for the unexpected result.
+Chiang Mai is a city with historical monument and you can enjoy beautiful landscape there.
+Following that, many tourists have been visiting the city.
+Therefore, there are more accessibility to healthcare facilities than that of other cities.
+Contrast to Chiang Mai, northeastern Thailand is more local.
+Extreme gap between mother reports and health record indirectly shows that there is short of the accessibility.
+
+Third, figure\@ref(fig:fig4) presents an interesting result.
+While mother's reports with different education are similar, as education level goes up from no education to higher, healthcare records increase.
+Also, non-immunization rate decreases as it goes up.
+Non-immunization rate in higher education group is only 0.6%, on the other hand, it is 29.4% for no education group.
+If healthcare facilities were available to all, this scheme would not exist.
+
+Lastly, figure\@ref(fig:fig5) represents immunization status along with religion.
+It shows that Buddhist got more immunization compared to that of Islam as well as healthcare records.
+Although Buddhist got more immunization, still its rate is mainly from mother's reports.
+One thing to notice here is that Islam in Thailand had non-immunization rate comparatively high.
+Like many variables above, we can suspect that there would be less accessibility to healthcare system in the Islamic communities.
 
 # Discussion
+In this s
 
-## First discussion point
+## What can we learn about 1987 Thailand healthcare system?
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## From results of analysis what should be enhanced?
 
-## Second discussion point
+## Weaknesses
 
-## Third discussion point
-
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
+## Next steps for future
 

### 2022-04-04 outputs/paper/paper.Rmd
Introduction ~ results writing edited

@@
 This is an important finding because it shows that there could be lack of trust toward healthcare system or shortage of healthcare supports in Thailand.
-Thus, it can indicate where or who to focus for the healthcare system to gain trust.
+Thus, it can indicate where or who to focus for the healthcare system to gain trust and to offer better services.
 With further research, we will be able observe how it has been improved since 1987, but for now we are going to focus on why the gap existed in 1987, Thailand.
-For detailed answer for why will be discussed in discussion session.
 
@@
 For instance, a data presented child and infant mortality with respect to participants' features.
-It showed the mortality rate with same variables that our data has.
+It even had the mortality rate with same variables that our data has.
 However, we thought that mortality alone could not be enough to show why the gap existed between healthcare system and mothers.
@@
 Calculating the percentage, it was 60% vs 22.8%.
-On the other hand, there seems comparatively similar cases between healthcare and mothers in urban areas.
+On the other hand, there seems comparatively similar cases reported from healthcare and mothers in urban areas.
 Lastly,immunization rate is higher in urban compared to rural areas.
@@
 This is because Islan, the northeast part of Thailand, is the largest region of Thailand, and urbanization in Thailand is relatively low.
-The graph shows very similar trends with \@ref(fig:fig1).
+The graph shows very similar trends with figure\@ref(fig:fig1).
 There were more mother's reports outside of Bangkok, and less immunization rate outside of Bangkok.
-On the other hand, comparatively equal cases are observed in Bangkok.
+On the other hand, comparatively equal cases were observed in Bangkok.
 One thing to notice is that percentage of mother's reports in Northeast is noticeably higher.
@@
 In addition to that, non immunization rate decreases.
-One thing to notice is that higher education you have in Thailand, there existed more immunization rate.
+Another thing to notice here is that higher education you have in Thailand, there existed more immunization cases.
 For instance, people with higher education shows immunization rate close to 100%.
@@
 At the beginning of introduction, we talked about small drawback in religion, which is other religions except Buddhisms and Islam were not collected.
-Moreover, majority of Thai people believes in Buddhism \@ref(fig:fig1), thus in the graph figure\@ref(fig:fig5), you can observe that there existed more cases in Buddhism than Islam.
+Moreover, majority of Thai people believes in Buddhism figure\@ref(fig:fig1).
 As we have observed up to this point, similar to other variables, there existed more mother's report cases than that of healthcare with no exception to religion.
@@
 ```
+
 ```{r fig4,echo=FALSE, fig.cap = "Immunization cases between education"}
@@
 # Results
-Results will likely require summary statistics, tables, graphs, images, and possibly statistical analysis or maps.
-To be clear, you should also have text associated with all these aspects.
-Show the reader the results by plotting them.
-Talk about them.
-Explain them.
-That said, this section should strictly relay results.
 
@@
 Let's take a look at figure\@ref(fig:fig6), which is the total result of immunization reports.
-This graph shows that how different immunization rate between healthcare and mother reports are among 2872 participants.
+This graph shows that how different immunization rate between healthcare and mother reports were among 2872 participants.
 58.9 percentage of immunization was reported by mothers, approximately 1691 people, 26.0 percentage for healthcare, approximately 747 people and finally 15.1 percentage for non-immunization which is approximately 434 people.
-With this numbers in mind, we are going to analyze why this phenomena occurred in Thailand with two focuses; the gap between healthcare records and mother's reports and non-immunization rate
+With this numbers in mind, we are going to analyze why this phenomena occurred in Thailand focusing on two main points; the gap between healthcare records and mother's reports as well as non-immunization rate
 
@@
 Following that, non immunization rate in rural areas is 17.2% which is more than 3 times of non immunization rate in urban, 5.3%.
-This two gaps indicate that there needs more healthcare facilitates.
-In addition to that, percentage of mother's reports in rural areas is not
-low. This shows that there existed accessibility to vaccines in rural areas. Thus, we also conclude that lack of trust toward healthcare system could potentially affect the gap as well.
+This two gaps indicate that there needs more healthcare facilitates in rural areas.
+However, percentage of mother's reports in rural areas is not low.
+This indirectly shows that there existed accessibility to vaccines in rural areas.
+Thus, we also concluded that lack of trust toward healthcare system could potentially influence the gap as well.
 
 Second, from figure\@ref(fig:fig3), regional based immunization rate shows very similar trends with that of communities.
-All over the regions, there are more mother's reports than healthcare records.
-For some specific region such as South, Northeast and Central, the gap is wider than the other two.
-Even there were more participants who answered non-immunization than health reports in south.
-One thing to notice from this graph is North part.
+All over the regions, there were more mother's reports than healthcare records.
+For some specific region such as South, Northeast and Central, the gap between mothers' reports and health records was wider than the others.
+Also, there were more participants who answered non-immunization status than health reports in south.
+Another interesting thing to notice from this graph is the North part.
 Northern Thailand shows very similar trend with Bangkok unlike other regions.
-We suspect the existence of city, Chiang Mai for the unexpected result.
+We suspect the city, Chiang Mai for the unexpected result.
 Chiang Mai is a city with historical monument and you can enjoy beautiful landscape there.
 Following that, many tourists have been visiting the city.
-Therefore, there are more accessibility to healthcare facilities than that of other cities.
+Therefore, there were more accessibility to healthcare facilities other cities outside of Bangkok.
 Contrast to Chiang Mai, northeastern Thailand is more local.
-Extreme gap between mother reports and health record indirectly shows that there is short of the accessibility.
+Following that, people in Chiang Mai could feel more vulnerable to virus or sensitive regarding it, therefore more willing to get vaccine for their children.
+In addition to that, Chiang Mai has one extra resource, which is tourist, so there were higher chances for them to get into middle class.
+This could lighten the burden for household spending.
 
-Third, figure\@ref(fig:fig4) presents an interesting result.
-While mother's reports with different education are similar, as education level goes up from no education to higher, healthcare records increase.
-Also, non-immunization rate decreases as it goes up.
+Third, figure\@ref(fig:fig4) presents very interesting point.
+While mother's reports no matter what educations you had in Thailand was uniform, as education level goes up from no education to higher, healthcare records increase.
+In addition to that, non-immunization rate decreases depending on your education.
 Non-immunization rate in higher education group is only 0.6%, on the other hand, it is 29.4% for no education group.
 If healthcare facilities were available to all, this scheme would not exist.
+We could deduce that having vaccine at healthcare facilities could be burden to some groups.
+Yet, we cannot be 100% certain about this result because we could not find relation between education level and income.
+This point could also be interpreted as lack of trust among lower education level groups.
 
@@
 Although Buddhist got more immunization, still its rate is mainly from mother's reports.
-One thing to notice here is that Islam in Thailand had non-immunization rate comparatively high.
+One thing to notice here is that non-immunization rate for Islam is comparatively high.
 Like many variables above, we can suspect that there would be less accessibility to healthcare system in the Islamic communities.
 
+To sum up, all of variables pointed same thing: need for more healthcare system in 1987 Thailand, or unbalance of healthcare system between regions, communities, cities, and religion.
+Furthermore, from some variables such as education level, we could find that some specific groups would not believe healthcare system 100%.
+
 # Discussion
-In this s
+In this session, we are going to explore remained and unanswered questions from results session.
 

### 2022-04-04 outputs/paper/paper.Rmd
discussion writing

@@
 # Introduction
-Trust is a big matter in this world.
-Especially when you need assistance in fields that you are unfamiliar with, trust is the best thing that you can rely on.
-For instance, if you need a lawyer, the best thing that you can do is to trust your lawyer, and be 100% honest.
+Trust is a very important but also a big issue in this world.
+Especially when you need assistance in fields that you are unfamiliar with and require help from others, trust is the best thing that you can rely on.
+For instance, if you need a legal advice, the best thing that you can do is to trust your lawyer, and be 100% honest.
 In medical field, trust is directly related to your life.
@@
 ## Weaknesses 
-
+Dataset does not have wide variety of information, more categories such as more variety on religion, additional information such as household income, number of hospitals in each region, and how easy to access to those hospitals, especially for rural areas, with worse public transportation.
 ## Next steps for future

### 2022-04-04 outputs/paper/paper.Rmd
discussion update and spelling check

@@
 Especially when you need assistance in fields that you are unfamiliar with and require help from others, trust is the best thing that you can rely on.
-For instance, if you need a legal advice, the best thing that you can do is to trust your lawyer, and be 100% honest.
+For instance, if you need a legal advice, the best thing that you can do is to trust your lawyer and be 100% honest.
 In medical field, trust is directly related to your life.
 We are certain that you have observed that many people have been refusing to get COVID-19 vaccines.
-Then, we started to wonder whether the COVID-19 vaccine controversy is similar to other vaccines that safety are proved and guaranteed such as BCG vaccine for preventing tuberculosis.
+Then, we started to wonder whether the COVID-19 vaccine controversy is similar to other vaccines that safety is proved and guaranteed such as BCG vaccine for preventing tuberculosis.
 It is true that we no longer have doubts against them.
-However, if you move sight to developing country in 1980~1990s, situation would certainly different because of lack of well constructed healthcare system or other reasons.
+However, if you move sight to developing country in 1980~1990s, situation would certainly different because of lack of well-constructed healthcare system or other reasons.
 This curiosity triggered us to start this research.
@@
 This paper is about children immunization reports in 1987, Thailand.
-Specifically how the rate differs between communities, regions, people with different education levels and religion.
+Specifically, how the rate differs between communities, regions, people with different education levels and religion.
 Along with that, its cases are divided into reports from mothers and healthcare.
@@
 Following that, we made a decision that combining other variables would cause bias in this research.
-The data we chose presented cases of children immunization status between communities(urban and rural), region(north,northeast,central,south and Bangkok), education level(no education, primary, secondary and higher), religion: (Buddhist and Islam), and where they were reported, or whether  children did not get one or not.
+The data we chose presented cases of children immunization status between communities (urban and rural), region(north,northeast,central,south and Bangkok), education level(no education, primary, secondary and higher), religion: (Buddhist and Islam), and where they were reported, or whether  children did not get one or not.
 For a small drawback, other religions such as Christianity was excluded since majority of Thai believe in Buddhism and rest believe in Islam.
@@
 On the other hand, there seems comparatively similar cases reported from healthcare and mothers in urban areas.
-Lastly,immunization rate is higher in urban compared to rural areas.
+Lastly, immunization rate is higher in urban compared to rural areas.
 
@@
 Instead, they were from Northeast.
-This is because Islan, the northeast part of Thailand, is the largest region of Thailand, and urbanization in Thailand is relatively low.
+This is because Islam, the northeast part of Thailand, is the largest region of Thailand, and urbanization in Thailand is relatively low.
 The graph shows very similar trends with figure\@ref(fig:fig1).
@@
 If you look at figure\@ref(fig:fig4), you can observe that as education level goes up, gap between mother's report and healthcare is being filled.
-In addition to that, non immunization rate decreases.
+In addition to that, non-immunization rate decreases.
 Another thing to notice here is that higher education you have in Thailand, there existed more immunization cases.
@@
 
-At the beginning of introduction, we talked about small drawback in religion, which is other religions except Buddhisms and Islam were not collected.
+At the beginning of introduction, we talked about small drawback in religion, which is other religions except Buddhism and Islam were not collected.
 Moreover, majority of Thai people believes in Buddhism figure\@ref(fig:fig1).
@@
 58.9 percentage of immunization was reported by mothers, approximately 1691 people, 26.0 percentage for healthcare, approximately 747 people and finally 15.1 percentage for non-immunization which is approximately 434 people.
-With this numbers in mind, we are going to analyze why this phenomena occurred in Thailand focusing on two main points; the gap between healthcare records and mother's reports as well as non-immunization rate
+With this numbers in mind, we are going to analyze why these phenomena occurred in Thailand focusing on two main points: the gap between healthcare records and mother's reports as well as non-immunization rate
 
@@
 Percentage of healthcare records for urban is 41.5% and for rural is 22.8%.
-Following that, non immunization rate in rural areas is 17.2% which is more than 3 times of non immunization rate in urban, 5.3%.
-This two gaps indicate that there needs more healthcare facilitates in rural areas.
+Following that, non-immunization rate in rural areas is 17.2% which is more than 3 times of non-immunization rate in urban, 5.3%.
+These two gaps indicate that there needs more healthcare facilitates in rural areas.
 However, percentage of mother's reports in rural areas is not low.
@@
 We suspect the city, Chiang Mai for the unexpected result.
-Chiang Mai is a city with historical monument and you can enjoy beautiful landscape there.
+Chiang Mai is a city with historical monument, and you can enjoy beautiful landscape there.
 Following that, many tourists have been visiting the city.
@@
 ## What can we learn about 1987 Thailand healthcare system?
+We learn that majority of the immunization report has been done by mother's claim instead of health record from a hospital.
+World Health Organization Reported that the child mortality rate in the 1980s were around 50%.
+Which indicates that the many of the mother's claim of receiving immunization could be false.
+WHO also reported that the Thailand government started investing on access to health care services to rural regions which would not be available for children in 1987.
+We can see from \@ref(fig:fig2) and \@ref(fig:fig3) that while both urban and rural regions have high number of mother's report, urban areas show children have immunization on their health record while rural areas have higher number of mother's claim of receiving immunization than health record.
+As observed in \@ref(fig:fig4), we can see that mothers with more education are more likely to immunize their children.
+We also can observe that number of mother's report decreases as level of mother's education increases.
+This shows the importance of education, especially on health care is for health of children.
+We can also observe from \@ref(fig:fig1) that majority of mothers have maximum of primary education, which is a huge concern for healthcare according to this dataset.
 
-## From results of analysis what should be enhanced?
+## From results of analysis, what should be enhanced?
+It clearly shows that Thailand, especially in the rural regions in 1987 required more health care infrastructure.
+As WHO reported that the Thailand government started investing more on primary health care services in the rural area in the 1980s, we expect to see gradual changes for updated versions of the dataset.
+Another aspect that needs improvement is education, we observed that parents' education is important for immunization of children.
 
 ## Weaknesses 
-Dataset does not have wide variety of information, more categories such as more variety on religion, additional information such as household income, number of hospitals in each region, and how easy to access to those hospitals, especially for rural areas, with worse public transportation.
+* Dataset does not have wide variety of information, more categories such as more variety on religion, additional information such as household income, number of hospitals in each region, and how easy to access to those hospitals, especially for rural areas, with worse public transportation.
+* Dataset contained some errors where the dataset which is in percentage, does not add up to 100% when it is supposed to.
 ## Next steps for future
@@
 https://www.statista.com/statistics/269967/urbanization-in-the-united-states/
+“Primary Health Care Systems (PRIMASYS).” Accessed April 4, 2022. https://www.who.int/alliance-hpsr/projects/alliancehpsr_thailandprimasys.pdf.

### 2022-04-05 outputs/paper/paper.Rmd
Next steps for futre and discussion edited

@@
 * Dataset does not have wide variety of information, more categories such as more variety on religion, additional information such as household income, number of hospitals in each region, and how easy to access to those hospitals, especially for rural areas, with worse public transportation.
-* Dataset contained some errors where the dataset which is in percentage, does not add up to 100% when it is supposed to.
+* Dataset contained some errors where the dataset which is in percentage, does not add up to 100% when it is supposed to. Therefore, accuracy of analysis is not perfect.
+
 ## Next steps for future 
+As WHO claimed gradual improvement in healthcare system in Thailand, analysis of similar survey in recent years will become good indicator whether Thailand government has succeed reformation of healthcare system or not.
+Furthermore, with the analysis, we will be able to observe which is needed further support or not.
+Current Thailand has been experiencing exponential growth in economics, following that we expect that the healthcare system has been improved much.
 

### 2022-04-05 outputs/paper/paper.Rmd
subtitle grammer edited

@@
 title: "The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]"
-subtitle: "Why there exists gap between health system and mother's report for immunization"
+subtitle: "Why there existed gap between health system and mother's report for immunization"
 author: 

### 2022-04-05 outputs/paper/paper.Rmd
Result session edited

@@
 
-To sum up, all of variables pointed same thing: need for more healthcare system in 1987 Thailand, or unbalance of healthcare system between regions, communities, cities, and religion.
-Furthermore, from some variables such as education level, we could find that some specific groups would not believe healthcare system 100%.
+To sum up, all of variables pointed same direction: need for better healthcare system in 1987 Thailand, or unbalance of healthcare system between regions, communities, cities, and religion.
+Moreover, from some variables such as education level, we could find that some specific groups did not trust the healthcare system 100%.
+Combining all weakness in healthcare system in Thailand, it presents unexpected result from contemporary thought, which is immunization status was inclined to mother more than healthcare facilities.
 

### 2022-04-05 outputs/paper/paper.Rmd
appendix session deleted
discussion section update

--- 2022-04-05 outputs/paper/paper.Rmd
@@
 As WHO reported that the Thailand government started investing more on primary health care services in the rural area in the 1980s, we expect to see gradual changes for updated versions of the dataset.
-Another aspect that needs improvement is education, we observed that parents' education is important for immunization of children.
+Another aspect that needs improvement is education, we observed that parents' education is important for immunization of children, and considering that the significant number of mothers do not continue with their education after primary school, more investment in learning infrastructure should have been considered by the Thailand government.
+For better understanding of these issues, more detailed survey and research on healthcare and education infrastructure should be conducted.
 

### 2022-04-05 outputs/paper/paper.Rmd

--- 2022-04-05 outputs/paper/paper.Rmd
@@
 
-\appendix
-
-# Appendix {-}
-
-# Additional details
-
-\newpage
-
 # References

### 2022-04-05 outputs/paper/paper.Rmd
reference fix

@@
 # References
-https://www.statista.com/statistics/455942/urbanization-in-thailand/
-https://www.statista.com/statistics/269967/urbanization-in-the-united-states/
+O'Neill, Aaron. “Thailand - Urbanization 2010-2020.” Statista, February 2, 2022. https://www.statista.com/statistics/455942/urbanization-in-thailand/.
+
+O'Neill, Aaron. “United States - Urbanization 2020.” Statista, February 2, 2022. https://www.statista.com/statistics/269967/urbanization-in-the-united-states/.
+
 “Primary Health Care Systems (PRIMASYS).” Accessed April 4, 2022. https://www.who.int/alliance-hpsr/projects/alliancehpsr_thailandprimasys.pdf.

### 2022-04-05 outputs/paper/paper.Rmd
code cleaning

@@
 ```{r fig2,echo=FALSE, fig.cap = "Immunization cases between communities"}
-#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
 urban_rural %>%
@@
 ```{r fig3,echo=FALSE, fig.cap = "Immunization cases between region"}
-#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
 region %>%
@@
 ```{r fig4,echo=FALSE, fig.cap = "Immunization cases between education"}
-#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
 education %>%
@@
 ```{r fig5,echo=FALSE, fig.cap = "Immunization cases between religion"}
-#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
 religion %>%

### 2022-04-05 scripts/01-gather_data.R

@@ -16,7 +16,6 @@ get_data <- function(text){
   
   immune_data <- immune_data[-c(1:7),]
   immune_data <- immune_data[-c(19:20),]
-  #immune_data <- extract(immune_data, raw_text, into=c('v1', 'v2'), '(\\d+)(\\D+)', convert=TRUE)
   
   # Split columns
   immune_data <-
@@ -38,10 +37,7 @@ get_data <- function(text){
     )
   
   immune_data <- immune_data[complete.cases(immune_data),] |> 
-    #select("Health_Record", "Mother's_Report", "Received_Immunization", "Not_Received_Immunization", "Total_Percent", "Number_of_Children") |>
     mutate_at(vars(Health_Record, Mothers_Report, Received_Immunization, Not_Received_Immunization, Total_Percent, Number_of_Children), ~str_remove_all(., ",")) |>
-    #mutate_at(vars(Health_Record, Mothers_Report, Received_Immunization, Not_Received_Immunization, Total_Percent, Number_of_Children), ~str_replace(., "_", "0")) |>
-    #mutate_at(vars(Health_Record, Mothers_Report, Received_Immunization, Not_Received_Immunization, Total_Percent, Number_of_Children), ~str_replace(., "-", "0")) |>
     mutate_at(vars(Health_Record, Mothers_Report, Received_Immunization, Not_Received_Immunization, Total_Percent, Number_of_Children), ~as.double(.))
   
   immune_data[8, 1] = "No Education"
